An analysis on outbreak management in Toronto Health Institutions from 2020 - 2022

### 2023-02-03 outputs/paper/paper.qmd
finalize and polish paper

  1. Outbreak setting: the type of facility, in terms of the type of healthcare provided, including Respiratory, Enteric (Gastroenteric), and Other
  2. Type of Outbreak: the mode of transmission classification description of the outbreak
  3. Causative & Etiological Agent: the aetiological agent(s) that have been identified from one or more outbreak-related cases
  4. Date Outbreak Began & Date Declared Over
  5. Active Status
  6. Institution Name & Address

@@

  When examining the correlation between the outbreak type and the setting, it is noticeable that the majority of outbreaks happened in Long-term Care Housings (LTCH). In 2020, those LTCHs witnessed 20 cases of Enteric outbreak and 296 cases of Respiratory outbreak. In 2021, the number of outbreak dropped down to 187 cases in both type, while that of in 2022 increased to more than 450 cases. Another notable detail to point out is that other types of outbreak only occurred in the Acute Care division of the hospitals. In 2022, Toronto also encountered the emergence of outbreak in Transitional Care with 9 cases. It is also apparent that hospital settings ceased to report cases for Enteric type of outbreak from 2021, on the other hand received more cases on respiratory diseases. (@tbl-setting)

>>>>

  1. Outbreak setting: the type of facility, in terms of the type of healthcare provided
  2. Type of Outbreak: the mode of transmission classification description of the outbreak, including Respiratory, Enteric (Gastroenteric), and Other
  3. Causative & Etiological Agent: the aetiological agent(s) that have been identified from one or more outbreak-related cases
  4. Date Outbreak Began & Date Declared Over
  5. Active Status
  6. Institution Name & Address

@@

  When examining the correlation between the outbreak type and the setting, it is noticeable that the majority of outbreaks happened in Long-term Care Housings (LTCH). In 2020, those LTCHs witnessed 20 cases of Enteric outbreak and 296 cases of Respiratory outbreak. In 2021, the number of outbreak dropped down to 187 cases in both type, while that of in 2022 increased to more than 450 cases. Another notable detail to point out is that other types of outbreak only occurred in the Acute Care division of the hospitals. In 2022, Toronto also encountered the emergence of outbreak in Transitional Care with 9 cases, all of which caused by Respiratory disease. It is also apparent that hospital settings ceased to report cases for Enteric type of outbreak from 2021, on the other hand received more cases on respiratory diseases. (@tbl-setting)
